--- 
title: "比較経営論"
author: "飯島高雄"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_book:
    includes:
      in_header: preamble.tex
      latex_engine: xelatex
      citation_package: natbib
    keep_tex: yes
  bookdown::gitbook:
    split_by: section+number
  bookdown::epub_book: default
documentclass: book
link-citations: yes
bibliography:
- book.bib
- packages.bib
site: bookdown::bookdown_site
biblio-style: apalike
---

# はじめに

　経営は外部環境に依存する。経営に最善モデルはない。
　最適なモデルは国によって異なる。政治・文化が異なるから。
　同じ国でも時代によって異なる。経済発展の程度が異なるから。

## 経営における文脈と外部環境（仮） {#context}

　内部と外部の話はここでする。




```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->


# 経営システムの比較基準 {#management}

Placeholder


## マネジメントの基礎
### Taylorの科学的管理法 　
### Fayolの管理過程論
## 文化
### Hofstede
### Hallの文脈
## 政治体制・法制度
### 政治体制   　
### 法制度
## 経済システム

<!--chapter:end:02-management.Rmd-->


# アメリカの経営システム {#usa}

Placeholder


## アメリカの文化・政治・経済
### 文化
### 政治システム・法制度
### 経済システム
## アメリカ企業の経営者
### 選抜・移動
### 報酬
### 教育
## アメリカ企業のマネジメント
### 計画
### 組織化
### 指揮・調整
### 統制

<!--chapter:end:03-usa.Rmd-->


# 日本の経営システム {#japan}

Placeholder


## 日本の文化・政治・経済
### 文化
### 政治システム・法制度
### 経済システム
## 日本企業の経営者
### 選抜・移動
### 報酬
### 教育
## 日本企業のマネジメント
### 計画
### 組織化
### 指揮・調整
### 統制

<!--chapter:end:04-japan.Rmd-->


# アジアの経営システム {#asia}

Placeholder


## アジアの文化・政治・経済
### 文化
### 4.1.2　政治システム・法制度
### 4.1.3　経済システム
## アジア企業の経営者
### 選抜・移動
### 報酬
### 教育
## アジア企業のマネジメント
### 4.3.1　計画
### 組織化
### 指揮・調整
### 統制

<!--chapter:end:05-asia.Rmd-->

# おわりに {#conclusion} 

We have finished a nice book.

<!--chapter:end:06-conclusion.Rmd-->

